---
title: "Save"
output: html_document
date: "2023-10-10"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r, message=FALSE}

libs_1<-c("tidyverse","knitr","psych","reshape2","rmarkdown")

#data manipulation/exploration
libs_2<-c("readxl","readr","tidyr","GGally","naniar","readr")


# plotting
libs_3<-c("ggplot2","viridis","ggpubr","cowplot")#,"ggthemr") 

#ggpubr = package for publishing
#cowplot=  #to create compounded figures

#tables
libs_4<-c("dplyr","stargazer","xlsx","ggplot2","scales","extrafont","writexl")


libs<-c(libs_1,libs_2,libs_3,libs_4)

lapply(libs,require, character.only=TRUE)

library(dplyr)
library(purrr)
library(gridExtra)
```

```{r}
getwd()

Background_ele<-read.delim("211008_0.1M_NaCl_0.05mL_min.TXT",header = TRUE, sep = "")

Background_ele<-data.frame(Background_ele[1:85,])

Background_ele[] <- lapply(Background_ele, function(x) as.numeric(as.character(x)))

#write_xlsx(Background_ele,"/Users/soliverfusi/OneDrive/Desktop/Fusi/Acid_Base_Titration/Titration/Background_ele.xlsx")
```

```{r}
files <- list.files("Base_Acid_Separate_Titration", full.names = TRUE)
str(files)
```

### Gathering Titration Data

```{r}

the_names<- data.frame(list.files(path="Base_Acid_Separate_Titration", pattern="*.TXT", full.names=TRUE)) 

colnames(the_names)=("ID")

the_names_1<-the_names%>%
  mutate(ID=substr(ID, 30,41))


list_1 <- list.files(path="Base_Acid_Separate_Titration", pattern="*.TXT", full.names=TRUE) %>% 
  lapply(read.csv,header=TRUE, sep="",col.names=c("Sample","Vol_Titrant","pH","Time_s","dpH_dt")) %>%
  lapply(head,-28)

#converts the "oo" chatacter into NA, and the remainder of the dataframe into numeric
list_1 <- lapply(list_1, function(d) {
  d[1:5] <- lapply(d[1:5], as.numeric); d
  })

saveRDS(list_1, file="Titration_together.rds")
```

\*currently choosing to retain things as a list because the length of each titration is different

-   metadata: starts with "Date" and ends with " Status: 128" and is the last 22 lines

### Mol OH-, Concentration H+, OH-, Volume Solution, Apparent Net Proton Charge

-   H+ = (for now) 10\^-pH

```{r}
#defining simplified relationship between pH and [H+]


mol_OH_or_H_added_func<-function(x){
  (0.1*x)/1000
}

ten_to<-function(x){
  10^-x
}

conc_OH_func<-function(x){
  (10^-14)/(10^-x)
}

vol_sol_func<-function(x){
  (30+x)/1000
}

net_app_H_func <- function(dataframe) {
  net_app_H<-as.data.frame(((-1*dataframe$H_Conc*dataframe$vol_soln)-dataframe$mol_OH+(dataframe$OH_Conc*dataframe$vol_soln))*1000)
  #return(data.frame(net_app_H = net_app_H))
}

#mol_OH or H added
mol_OH_or_H<-list_1 %>%
  lapply("[",2) %>%
  lapply(mol_OH_or_H_added_func) 
  
H_Conc<- list_1 %>%
  lapply("[",3) %>%
  lapply(ten_to)

OH_Conc<- list_1 %>%
  lapply("[",3) %>%
  lapply(conc_OH_func)

vol_soln<-list_1 %>%
  lapply("[",2) %>%
  lapply(vol_sol_func) 

list_2<-mapply(cbind, mol_OH_or_H, H_Conc,OH_Conc,vol_soln, SIMPLIFY=FALSE)
names_col<-c("mol_OH_or_H","H_Conc","OH_Conc","vol_soln")
list_2<-lapply(list_2, setNames, names_col)

list_3<-mapply(cbind,list_1,list_2, SIMPLIFY=FALSE)

# Call the custom function using lapply to apply it to each dataframe
net_app_H<- lapply(list_3, net_app_H_func)
net_app_H<-lapply(net_app_H, setNames,"net_app_H")
  
list_4<-mapply(cbind,list_3,net_app_H, SIMPLIFY=FALSE)
#lapply("[", , names_col) %>% #extracts the 4 columns 
  #explanation: https://stackoverflow.com/questions/47443365/how-to-extract-certain-columns-from-a-list-of-data-frames 

```

```{r}
# Sample 'names' dataframe

naming<-as.character(seq(1,74))

names_df <- data.frame(
  dataframe = naming,
  identity = the_names_1
)


# Create an empty list to store the named dataframes
list_5 <- list()

# Assign names to the dataframes in the results list
for (i in 1:length(list_4)) {
  dataframe_name <- names_df$ID[i]
  list_5[[dataframe_name]] <- list_4[[i]]
}

# Combine the result dataframes and add a column to distinguish between dataframes

#bind_rows function in the dplyr package is used to combine multiple dataframes into a single dataframe by stacking them on top of each other.

#.id = "ID" specifies that a new column named "ID" should be added to the combined dataframe. This column will contain information about the source dataframe for each 

net_app_combined <- bind_rows(list_5, .id = "SSN") 

output_vars<-read_excel("/Users/soliverchefusi/Library/CloudStorage/OneDrive-Personal/Desktop/Fusi/Sorption/AK_to_AO_Isotherm/Isotherm_FTIR/IR_Dependent_Variables.xlsx")


# Function to find the matching sample ID
find_matching_sample <- function(id, df2) {
  for (sample_id in df2$SSN) {
    if (grepl(sample_id, id)) {
      return(sample_id)
    }
  }
  return(NA)
}

# Merge df1 and df2 based on partial string matching
df_6 <- net_app_combined %>%
  mutate(matched_sample = sapply(SSN, find_matching_sample, output_vars))

# Merge the data based on the matched_sample column
df_6 <- left_join(df_6, output_vars, by = c("matched_sample" = "SSN"))

# Remove the temporary matched_sample column
df_6 <- df_6 %>%
  select(-matched_sample)

```

## Correcting for Ionic Strength

Libraries

```{r}
library(CHNOSZ)
library(readxl)
```

```{r}
Ions <- read_excel("Base_Acid_Separate_Titration/End_Anion_Concentration.xlsx")

#I think I accidentally mislabeled the sample NaOH, it should actually be the HCl sample (because NaOH wouldn't have Cl in it)

Ions_1<-Ions[c(14:93),c(2,7)]
colnames(Ions_1)<-c("SSN","Cl_mg_L")

Ions_2<-Ions[c(95:98),c(2,7)]
colnames(Ions_2)<-c("SSN","Cl_mg_L")

Ions_1 <- Ions_1 %>% filter(SSN != "MQ") %>%
  filter(SSN != "RESET")

```

Converting Units from mg/L to mol Cl

```{r}

MW_Cl <- 35.453

Ions_1 <- Ions_1 %>% mutate(Cl_mg_L = as.numeric(Cl_mg_L)) %>%
  mutate(Cl_mol_L = Cl_mg_L / MW_Cl/1000/3) 

#changing the ID format from, e.g. AK05A to AK_05_A
Ions_1$SSN <- gsub("([A-Z]+)(\\d+)([A-Z]+)", "\\1_\\2_\\3", Ions_1$SSN)

Ions_2 <- Ions_2 %>% mutate(Cl_mg_L = as.numeric(Cl_mg_L)) %>%
  mutate(Cl_mol_L = Cl_mg_L / MW_Cl/1000/3)

#TEMPORARILY: dividing by this factor of 3 until I can identify the source of what seems like an error

```

Currently noticing that the NaCl solution, for instance, which should have a concentration of 0.1M is reading about 0.35M ... unclear if this is a dilution error or what.

-   So, there seems to be an issue of a factor of 3...

```{r}

#Adding the Cl concentration to the main dataframe ... 

df_7 <- df_6 %>%
  mutate(matched_sample = sapply(SSN, find_matching_sample, Ions_1))

# Merge the data based on the matched_sample column
df_7 <- left_join(df_7, Ions_1, by = c("matched_sample" = "SSN"))

# Remove the temporary matched_sample column
df_7 <- df_7 %>%
  select(-matched_sample) %>%
  select(-Cl_mg_L)
```

TEMPORARILY CREATING AN Na COLUMN WHILE WE AWAIT THE CATION DATA (0.98\* Cl column)

```{r}

df_7<- df_7 %>%
  mutate(Na_mol_L = 0.98*Cl_mol_L)
```

## Calculating Activity Coefficient

```{r}


net_app_H_func_corrected <- function(dataframe) {
  net_app_H_corrected<-as.data.frame(((-1*dataframe$H_Conc_corrected*dataframe$vol_soln)-dataframe$mol_OH_or_H+(dataframe$OH_Conc*dataframe$vol_soln))*1000)
  #return(data.frame(net_app_H = net_app_H))
}

#correcting formula for mol strong acid addec (here )
net_app_H_func_acid_corrected <- function(dataframe) {
  net_app_H_corrected<-as.data.frame(((-1*dataframe$H_Conc_corrected*dataframe$vol_soln)+dataframe$mol_OH_or_H+(dataframe$OH_Conc*dataframe$vol_soln))*1000)
  #return(data.frame(net_app_H = net_app_H))
}

df_7 <- df_7 %>%
  mutate(Ionic_Strength = 0.5 * (((1^2)*Na_mol_L)+((-1)^2*Cl_mol_L))) %>%
  mutate(gamma = 10^(-0.509*sqrt(Ionic_Strength))) %>%
  mutate(H_Conc_corrected = (10^((-1)*pH))/gamma)

#correcting for both activity and using the two diff equations depending on whether it's and acid or a base titration 

df_ACID<-df_7 %>%
    filter(str_detect(SSN,"_ACID")) %>%
  mutate(net_app_H_corrected = net_app_H_func_acid_corrected(.)) %>%
  rename_at(26, ~ "net_app_H_corrected") %>% 
  mutate(net_app_H_corrected = as.numeric(unlist(net_app_H_corrected)))
 # rename_with(~ "net_app_H_corrected", .cols = 26)


df_BASE<-df_7 %>%
    filter(str_detect(SSN,"_BASE")) %>%
  mutate(net_app_H_corrected = net_app_H_func_corrected(.)) %>%
  rename_at(26, ~ "net_app_H_corrected") %>% 
  mutate(net_app_H_corrected = as.numeric(unlist(net_app_H_corrected)))

df_8<-rbind(df_ACID,df_BASE)
df_8$SSN<-as.factor(df_8$SSN)

# Create a new column identifying type (AK) and ID (AK_05)
df_8$Type <- substr(df_8$SSN, start = 1, stop = 2)
df_8$Type_ox <- substr(df_8$SSN, start = 1, stop = 5)
df_8$AC_BA <- substr(df_8$SSN, start = 9, stop = 12)

```

### Plot of all duplicated of both acid and base titrations

```{r}

ALL_no_AL<-df_8 %>%
  filter (Type != "AL")

plot_all <- ggplot(ALL_no_AL, aes(x = pH, y = net_app_H_corrected, color=O_C)) +
  geom_point(shape=16, size=5) +
  scale_color_viridis()+
  labs(#title = "Combined Acid-Base Titration",
       x = "pH",
       y = "Proton Charge (mmol charge /g biochar)") +
    theme_bw()+
      #eliminates background, gridlines, and chart border
    theme(
      panel.border = element_rect(color = "black", fill = NA, size = 3),
      axis.text = element_text(color = "black", size = 18), 
      axis.ticks = element_line(color = "black", size = 1),
      axis.title = element_text(color = "black", size =20),
        plot.background = element_blank()
        ,panel.grid.major = element_blank()
        ,panel.grid.minor = element_blank()
    )
plot_all    
```

```         
```

```{r}

#subselecting the samples based on acid or base and replicate

titr_A_base<-df_8%>%
  filter(str_detect(SSN,"A_BASE"))

titr_B_base<-df_8%>%
  filter(str_detect(SSN,"B_BASE"))

titr_C_acid<-df_8%>%
  filter(str_detect(SSN,"C_ACID"))

titr_D_acid<-df_8%>%
  filter(str_detect(SSN,"D_ACID"))

```

### Blank Correction

```{r}
blank_NaCl<- read.csv("Base_Acid_Separate_Titration/Water_Blank.csv")


correct_sample_pH <- function(sample_pH1, sample_pH2, sample_mol1, sample_mol2, blank_data) {
  # Calculate the pH change in the sample titration
  pH_change_sample <- sample_pH2 - sample_pH1
  
  # Find the interpolated pH values in the blank data for sample_pH1 and sample_pH2
  interpolated_pH_blank <- spline(blank_data$mol_blank, blank_data$pH_blank, n = 1000)
  pH_blank1 <- interpolated_pH_blank$y[which.min(abs(interpolated_pH_blank$x - sample_mol1))]
  pH_blank2 <- interpolated_pH_blank$y[which.min(abs(interpolated_pH_blank$x - sample_mol2))]
  
  # Calculate the pH change in the blank titration
  pH_change_blank <- pH_blank2 - pH_blank1
  
  # Calculate the portion of titrant used to change the blank's pH
  fraction_used_in_blank <- pH_change_blank / pH_change_sample
  
  # Calculate the corrected pH in the sample
  corrected_sample_pH2 <- sample_pH2 - pH_change_sample * fraction_used_in_blank
  
  return(corrected_sample_pH2)
}

# Example usage
sample_pH1 <- 4
sample_pH2 <- 5
sample_mol1 <- 0.5
sample_mol2 <- 0.6
blank_data <- data.frame(
  mol_blank = c(0.05, 0.1, 0.15, 0.2, 0.25),  # Add your blank data points
  pH_blank = c(3, 3.4, 3.6, 3.8, 4.1)         # Corresponding pH measurements
)

corrected_sample_pH <- correct_sample_pH(sample_pH1, sample_pH2, sample_mol1, sample_mol2, blank_data)

```

## Plots

```{r}
library(RColorBrewer)
```

```{r}

plot_A_base <- ggplot(titr_A_base, aes(x = pH, y = net_app_H_corrected, color=O_C)) +
  geom_point() +
  scale_color_viridis()+
  labs(title = "Base Titration",
       x = "pH",
       y = "Net Apparent Proton Charge") +
  theme_minimal()
plot_A_base      
```

```{r}

plot_B_base <- ggplot(titr_B_base, aes(x = pH, y = net_app_H_corrected, color=O_C)) +
  geom_point() +
  scale_color_viridis()+
  labs(title = "Base Titration",
       x = "pH",
       y = "Net Apparent Proton Charge") +
  theme_minimal()
plot_B_base
```

```{r}

plot_C_acid <- ggplot(titr_C_acid, aes(x = pH, y = net_app_H_corrected, color=O_C)) +
  geom_point() +
  scale_color_viridis()+
  labs(title = "Acid Titration",
       x = "pH",
       y = "Net Apparent Proton Charge") +
  theme_minimal()
plot_C_acid
```

```{r}
plot_D_acid <- ggplot(titr_D_acid, aes(x = pH, y = net_app_H_corrected, color=O_C)) +
  geom_point() +
  scale_color_viridis()+
  labs(title = "Acid Titration",
       x = "pH",
       y = "Net Apparent Proton Charge") +
  theme_minimal()
plot_D_acid
```

## dpH

```{r}

df_9 <-df_8 %>%
  filter (Type != "AL")

plot_all_dpH <- ggplot(df_9, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  #facet_wrap(~ Type, scales = "free")+ 
  labs(#title = "Base Titration",
       x = "pH",
       y = "dpH/ d vol titrant") +
    theme_bw()+
      #eliminates background, gridlines, and chart border
    theme(
      panel.border = element_rect(color = "black", fill = NA, size = 3),
      axis.text = element_text(color = "black", size = 17), 
      axis.ticks = element_line(color = "black", size = 1),
      axis.title = element_text(color = "black", size =20),
        plot.background = element_blank()
        ,panel.grid.major = element_blank()
        ,panel.grid.minor = element_blank()
    )+
  scale_color_gradient(low = "yellow", high = "darkblue")
plot_all_dpH 

```

```{r}

ALL_Base <-df_8 %>%
  filter (AC_BA=="BASE",
          Type != "AL")

plot_ALL_Base <- ggplot(ALL_Base, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  #facet_wrap(~ Type, scales = "free")+ 
  labs(#title = "Base Titration",
       x = "pH",
       y = NULL) +
    theme_bw()+
      #eliminates background, gridlines, and chart border
    theme(
      panel.border = element_rect(color = "black", fill = NA, size = 3),
      axis.text = element_text(color = "black", size = 10), 
      axis.ticks = element_line(color = "black", size = 1),
      axis.title = element_text(color = "black", size =20),
        plot.background = element_blank()
        ,panel.grid.major = element_blank()
        ,panel.grid.minor = element_blank()
    )+
  scale_color_gradient(low = "yellow", high = "darkblue")
plot_ALL_Base
```

AK Base

```{r}

AK_B_base <-titr_B_base %>%
  filter (Type=="AK")

plot_B_base_dpH <- ggplot(AK_B_base, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  labs(title = "Base Titration",
       x = "pH",
       y = "dpH/") +
  theme_minimal()
plot_B_base_dpH
```

AM

```{r}

AM_B_base <-titr_B_base %>%
  filter (Type=="AM")

plot_B_base_dpH <- ggplot(AM_B_base, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  labs(title = "Base Titration",
       x = "pH",
       y = "dpH/") +
  theme_minimal()
plot_B_base_dpH
```

```{r}

AK_B_base <-titr_B_base %>%
  filter (Type=="AK" & SSN=="AK_05_B_BASE")

plot_B_base_dpH <- ggplot(AK_B_base, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  labs(title = "Base Titration",
       x = "pH",
       y = "dpH/") +
  theme_minimal()
plot_B_base_dpH
```

```{r}
AK_D_acid <-titr_D_acid %>%
  filter (Type=="AK")

plot_D_acid_dpH <- ggplot(AK_D_acid, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  labs(title = "Acid Titration",
       x = "pH",
       y = "dpH/d Vol titrant") +
  theme_minimal()
plot_D_acid_dpH
```

w/o AL

```{r}


ALL_Acid <-df_8 %>%
  filter (AC_BA=="ACID",
          Type != "AL")

plot_ALL_Acid <- ggplot(ALL_Acid, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  #facet_wrap(~ Type, scales = "free")+ 
  labs(#title = "Base Titration",
       x = "pH",
      y = "dpH/d vol titrant") +
    theme_bw()+
      #eliminates background, gridlines, and chart border
    theme(
      panel.border = element_rect(color = "black", fill = NA, size = 3),
      axis.text = element_text(color = "black", size = 10), 
      axis.ticks = element_line(color = "black", size = 1),
      axis.title = element_text(color = "black", size =20),
        plot.background = element_blank()
        ,panel.grid.major = element_blank()
        ,panel.grid.minor = element_blank()
    )+
  scale_color_gradient(low = "yellow", high = "darkblue")+
  guides(color=FALSE)
     
plot_ALL_Acid
```

```{r}
plot_ALL_Acid_facet <- ggplot(ALL_Acid, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  facet_wrap(~ Type, scales = "free")+ 
  labs(#title = "Base Titration",
       x = "pH",
       y = "dpH/") +
  theme_bw()+
      #eliminates background, gridlines, and chart border
    theme(
        plot.background = element_blank()
        ,panel.grid.major = element_blank()
        ,panel.grid.minor = element_blank()
    )+
  scale_color_gradient(low = "yellow", high = "darkblue")
plot_ALL_Acid_facet
```

```{r}

ALL_Base <-df_8 %>%
  filter (AC_BA=="BASE",
          Type !="AL")

plot_ALL_Base_facet <- ggplot(ALL_Base, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  facet_wrap(~ Type, scales = "free")+ 
  labs(#title = "Base Titration",
       x = "pH",
       y = "dpH/") +
  theme_bw()+
      #eliminates background, gridlines, and chart border
    theme(
        plot.background = element_blank()
        ,panel.grid.major = element_blank()
        ,panel.grid.minor = element_blank()
    )+
  scale_color_gradient(low = "yellow", high = "darkblue")
plot_ALL_Base_facet
```

```{r}

Acid_Base_plot <- grid.arrange(plot_ALL_Acid, plot_ALL_Base, ncol = 2)
```

```{r}

AK_D_acid <-titr_D_acid %>%
  filter (Type=="AK")

plot_D_acid_AK <- ggplot(AK_D_acid, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  labs(title = "Base Titration",
       x = "pH",
       y = "dpH/") +
  theme_bw()+
      #eliminates background, gridlines, and chart border
    theme(
        plot.background = element_blank()
        ,panel.grid.major = element_blank()
        ,panel.grid.minor = element_blank()
    )
plot_D_acid_AK

```

AM

```{r}
AM_D_acid <-titr_D_acid %>%
  filter (Type=="AM")

plot_D_acid_AM <- ggplot(AM_D_acid, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  labs(title = "Base Titration",
       x = "pH",
       y = "dpH/") +
  theme_bw()+
      #eliminates background, gridlines, and chart border
    theme(
        plot.background = element_blank()
        ,panel.grid.major = element_blank()
        ,panel.grid.minor = element_blank()
    )
plot_D_acid_AM
```

```{r}
AO_D_acid <-titr_D_acid %>%
  filter (Type=="AO")

plot_D_acid_AO <- ggplot(AO_D_acid, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  labs(title = "Base Titration",
       x = "pH",
       y = "dpH/") +
  theme_bw()+
      #eliminates background, gridlines, and chart border
    theme(
        plot.background = element_blank()
        ,panel.grid.major = element_blank()
        ,panel.grid.minor = element_blank()
    )
plot_D_acid_AO
```

```{r}

AL_D_acid <-titr_D_acid %>%
  filter (Type=="AL")

plot_D_acid_AL <- ggplot(AL_D_acid, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  labs(title = "Base Titration",
       x = "pH",
       y = "dpH/") +
  theme_bw()+
      #eliminates background, gridlines, and chart border
    theme(
        plot.background = element_blank()
        ,panel.grid.major = element_blank()
        ,panel.grid.minor = element_blank()
    )
plot_D_acid_AL
```

```{r}

plot_B_base_dpH <- ggplot(titr_B_base, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  labs(title = "Base Titration",
       x = "pH",
       y = "dpH/") +
  theme_minimal()
plot_B_base_dpH
```

```{r}

plot_all <- ggplot(df_8, aes(x = pH, y = dpH_dt, group =SSN, color=Type)) +
  geom_point()+
  #geom_line() +
  labs(#title = "Base Titration",
       x = "pH",
       y = "dpH/") +
  theme_classic2()
plot_all
```

```{r}

AK_all <- df_8 %>%
  filter (Type=="AK")

plot_AK_all <- ggplot(AK_all, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  #geom_line() +
  labs(#title = "Base Titration",
       x = "pH",
       y = "dpH/") +
  theme_classic2()
plot_AK_all
```

```{r}

AM_all_dpH <- df_8 %>%
  filter (Type=="AM")

plot_AM_all_dpH <- ggplot(AM_all_dpH, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  #facet_wrap(~ Type, scales = "free")+ 
  labs(#title = "Base Titration",
       x = "pH",
       y = "dpH/") +
    theme_bw()+
      #eliminates background, gridlines, and chart border
    theme(
      panel.border = element_rect(color = "black", fill = NA, size = 3),
      axis.text = element_text(color = "black", size = 10), 
      axis.ticks = element_line(color = "black", size = 1),
      axis.title = element_text(color = "black", size =20),
        plot.background = element_blank()
        ,panel.grid.major = element_blank()
        ,panel.grid.minor = element_blank()
    )+
  scale_color_gradient(low = "yellow", high = "darkblue")
plot_AM_all_dpH 
```

```{r}

AM_all_dpH <- df_8 %>%
  filter (Type=="AM")

plot_AM_all_dpH <- ggplot(AM_all_dpH, aes(x = pH, y = dpH_dt, group =SSN, color=O_C)) +
  geom_point()+
  geom_path(aes(group = 1), size = 1) +
  #facet_wrap(~ Type, scales = "free")+ 
  labs(#title = "Base Titration",
       x = "pH",
       y = "dpH/") +
    theme_bw()+
      #eliminates background, gridlines, and chart border
    theme(
      panel.border = element_rect(color = "black", fill = NA, size = 3),
      axis.text = element_text(color = "black", size = 10), 
      axis.ticks = element_line(color = "black", size = 1),
      axis.title = element_text(color = "black", size =20),
        plot.background = element_blank()
        ,panel.grid.major = element_blank()
        ,panel.grid.minor = element_blank()
    )+
  scale_color_gradient(low = "yellow", high = "darkblue")
plot_AM_all_dpH 
```

```{r}
Acid_Base_plot <- grid.arrange(plot_A_base, plot_D_acid, ncol = 2)
Acid_Base_plot
```

```{r}

combined_A_D <- rbind(titr_A_base, titr_D_acid)

plot_combined_A_D <- ggplot(combined_A_D, aes(x = pH, y = net_app_H_corrected, color=O_C)) +
  geom_point() +
  scale_color_viridis()+
  labs(title = "Acid Base Titration",
       x = "pH",
       y = "Net Apparent Proton Charge") +
  theme_minimal()
plot_combined_A_D
```

```{r}

combined_B_C <- rbind(titr_B_base, titr_C_acid)

plot_combined_B_C <- ggplot(combined_B_C, aes(x = pH, y = net_app_H_corrected, color=O_C)) +
  geom_point() +
  scale_color_viridis()+
  labs(title = "Acid Base Titration",
       x = "pH",
       y = "Net Apparent Proton Charge") +
  theme_minimal()
plot_combined_B_C
```

```{r}

AK_Only <- df_8%>%
    filter(str_detect(SSN,"AK_")) 


plot_combined_AK <- ggplot(AK_Only, aes(x = pH, y = net_app_H_corrected, color=O_C))+ #, size = SSN)) +
  geom_point() +
    scale_color_viridis()+
  
  labs(title = "AK: Softwood Pellet Acid-Base Titration",
       x = "pH",
       y = "Net Apparent Proton Charge (mmol charge/g biochar)") +
  theme_bw()+
      #eliminates background, gridlines, and chart border
    theme(
        plot.background = element_blank()
        ,panel.grid.major = element_blank()
        ,panel.grid.minor = element_blank()
    )+
  guides(size = FALSE)
plot_combined_AK
```

```{r}

AM_Only <- df_8%>%
    filter(str_detect(SSN,"AM_")) 


plot_combined_AM <- ggplot(AM_Only, aes(x = pH, y = net_app_H_corrected, color=O_C, size = SSN)) +
  geom_point() +
  labs(title = "Acid Base Titration",
       x = "pH",
       y = "Net Apparent Proton Charge") +
  theme_minimal()
plot_combined_AM
```

```{r}

AO_Only <- df_8%>%
    filter(str_detect(SSN,"AO_")) 

plot_combined_AO <- ggplot(AO_Only, aes(x = pH, y = net_app_H_corrected, color=O_C, size = SSN)) +
  geom_point() +
  labs(title = "Acid Base Titration",
       x = "pH",
       y = "Net Apparent Proton Charge") +
  theme_minimal()
plot_combined_AO
```
